Linear Regret Bounds for Polyhedral Surrogates

### 2021-05-11 notes/regret-bound.tex
lovasz
starting the regret lower bound

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\cite{rockafellar1997convex}.

@@

@@

>>>>

We say a surrogates $L$ is \emph{polyhedral} if it is piecewise linear and convex.
To introduce this definition more formally, let us recall some definitions from convex geometry.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
% A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\cite{rockafellar1997convex}.

@@

\subsection{Surrogate regret bound}

The primary focus of this paper is on surrogate regret bounds, which bound the excess target loss in terms of the excess surrogate loss.

\begin{definition}[Surrogate Regret Bound]\label{def:regret-bound}
  A \emph{surrogate regret bound} between target $\ell:\R\to\reals^\Y$ and surrogate $L:\reals^d\to\reals^\Y$, together with a link $\psi : \reals^d \to \R$, is the statement
  \begin{equation}
    \label{eq:regret-bound-general}
    \forall p\in\simplex, u\in\reals^d, \quad R_\ell(\psi(u),p) \leq \zeta(\, R_L(u,p) \,)~,
  \end{equation}
  for some function $\zeta : \reals_+ \to \reals_+$ which is continuous at $0$ and satisfies $\zeta(0) = 0$.
\end{definition}

@@

\section{Lower Bounds for Smooth Surrogates}

\begin{definition}[Strong Convexity and Strong Smoothness]
  Let $f:\reals^d\to\reals$ be a differentiable convex function.
  We say $f$ is $\alpha$-\emph{strongly convex} if
  \begin{equation}
    \label{eq:strong-convexity}
    \|\nabla f(x) - \nabla f(x')\|_2 \geq \alpha \|x-x'\|_2 \quad \forall x,x'\in\reals^d~.
  \end{equation}

\end{definition}

\begin{theorem}
  Let $L:\reals^d \to \reals^\Y_+$ be a surrogate such that for all $y\in\Y$, the function $L(\cdot)_y$ is differentiable, $\alpha$-strongly convex, and $\beta$-strongly smooth.\raft{I think differentiability follows from smoothness...}
\end{theorem}
